Gammapy: A Python package for gamma-ray astronomy

### 2022-12-03 src/text/4-project.tex
Add a paragraph about SWH (#67)
* Add the SWH reference

Signed-off-by: Bruno Khelifi <khelifi@in2p3.fr>

* Add the archive in SWH

Signed-off-by: Bruno Khelifi <khelifi@in2p3.fr>

* Delete gammapy-v1.0-paper.iml

* Delete .gitignore

* Delete profiles_settings.xml

* Delete vcs.xml

* Delete Project_Default.xml

* Delete misc.xml

* Delete modules.xml

Signed-off-by: Bruno Khelifi <khelifi@in2p3.fr>

>>>>

As many other softwares, \gammapy is also indexed in the SoftWare
Heritage\footenote{\url{https://www.softwareheritage.org/}} (SWH) archive~\cite{DBLP:conf/icms/Cosmo20},
whom ambition is to collect, preserve, and share all software that is publicly available in source code form.
SWH automatically scans open software repositories, like e.g. GitHub, and projects are archived in SWH by the
means of SoftWare Heritage persistent IDentifiers (SWHID), that are guaranteed to remain stable (persistent)
over time. The French open publication archive, HAL~\footenote{\url{https://hal.archives-ouvertes.fr/}},
is using the \gammapy SWHIDs to register our releases as scientific
product\footenote{\url{https://hal.archives-ouvertes.fr/hal-03713410v1}} of open science.
